\documentclass[a4paper,margin,line]{resume}
\usepackage[defblank]{paralist}
\usepackage{pdfpages}
\usepackage{anysize}
\usepackage[unicode]{hyperref}
\hypersetup{
	pdftitle={Victoria Weaver's Resume},
	pdfauthor={Victoria Weaver},
	pdfborder={0 0 0},
	unicode=true
}


\newcommand\textbox[1]{%
  \parbox{.333\textwidth}{#1}%
  }

\marginsize{0.375in}{1.875in}{0.375in}{0.175in}

\setdefaultitem{\footnotesize \textbullet}{}{}{}{}{}
\setdefaultleftmargin{0em}{}{}{}{}{}
\setdefaultenum{(a)}{(1)}{}{}{}{}

\newcommand{\rurl}[1]{\hfill {\footnotesize \url{#1}}}
\newcommand{\rdate}[1]{\hfill {\small #1}}
\renewcommand{\employer}[5]{ \item[#1] - #2 \rdate{#3} \\* #4 \rurl{#5} \\*}

\begin{document}
\name{\Large{Victoria Weaver} \hskip 0pt plus 2fil minus 0pt {\small{\href{mailto:vweaver2013@gmail.com}{vweaver2013@gmail.com} - (313) 207-3039}}}
\begin{resume}
\section{\mysidestyle Objective}
    To obtain a coop or internship position in the field of Computer Engineering for the Summer of 2017.
\section{\mysidestyle Work Experience}
	\begin{asparadesc}
        \employer{Critical Link LLC}{Syracuse, NY}{May 2016 - Present}{Engineering Intern}
        {http://criticallink.com/}
        \small
        Currently aiding in the research for application of Hall Effect sensors for proximity sensing.  
        Research includes possible concerns of the application, and design, implementation, and analysis of 
        test circuits.\smallskip\\
        Aiding in the development of the Android software for a bacteria-scanning device. Android 
        Studio is used to develop the application in Java. Main focus is on the user interface of the application.
        \normalsize
        \\
        \employer{Parsons Government Services}{Centreville, VA}{Summer 2015}{Personal Computer Support Tech Intern}
        {http://parsons.com/}
        \small
        Worked on Java back end development in an Eclipse environment with a focus on fixing existing 
        issues in a networking security application. Collaborated on the documentation of the installation 
        of a service for the project on a clean virtual machine running Ubuntu. Tested and verified 
        different components of the application and submitted defect tickets through JIRA.  Collaborated 
        in code reviews using Review Board.
        \normalsize
        \\
        \employer{Rochester Institute of Technology}{Rochester, NY}{Fall 2014}{Student Lab Instructor}
        {http://rit.edu/}
        \small
        Lab instructor, individual tutor, and grader of assignments for students enrolled in the 
        introductory computer science course sequence.
        \normalsize
        \\
        \employer{Rochester Institute of Technology}{Rochester, NY}{Summer 2014}{Student Developer}
        {http://rit.edu/}
        \small
        Worked on the development of a keyboard and screen reader compatible ``drag and drop" programming 
        environment.  Aided in the development of Inclusive Exploring Computer Science curriculum for 
        visually impaired students.
        \normalsize
        \\
    \end{asparadesc}

\section{\mysidestyle Education}
	\begin{compactdesc}
		\item[Rochester Institute of Technology] - Rochester, NY \rdate{August 2013 - Present} \\
            Major: Computer Engineering, Minor: Mathematics \rdate{GPA: 3.337} \\
            Graduation: December 2017
	\end{compactdesc}

\section{\mysidestyle Technical Skills \& Certifications}
    \begin{compactdesc}
		\item[Software] \begin{inparaenum} { \small
            VHDL,
            \LaTeX,
			Java,
			C,
            ARM and MIPS Assembly,
            Python
		} \end{inparaenum}
		\item[Hardware] \begin{inparaenum} { \small
			Soldering,
            Power Supplies,
            Multimeters,
            Oscilloscopes
		} \end{inparaenum}
        \item[Tools] \begin{inparaenum} { \small
            Git,
            Xilinx,
            ModelSim,
            Android Studio,
            PSpice,
            Altera Quartus II
        } \end{inparaenum}
        \item[Certifications] \begin{inparaenum} { \small
            Electrostatic Discharge (ESD) Certification, 2016   
        } \end{inparaenum}
	\end{compactdesc}

\section{\mysidestyle Personal Projects}
    \begin{asparablank}
        \item \href{http://github.com/VictoriaWeaver/}{http://github.com/VictoriaWeaver/}\\
        \item \textbf{MIPS-VHDL}: Implemented a portion of the MIPS assembly instruction set 
            architecture in VHDL.\\
        \item \textbf{Infrared Proximity Sensor}: Employed the use of infrared LEDs for proximity 
            sensing in conjunction with seven segment displays and a buzzer for visual and auditory 
            feedback.\\
        \item \textbf{LED Table}: Constructed a programmable matrix of LEDs in a custom wooden 
            case with a diffused Plexiglas cover to make various patterns and animations.\\
        \item \textbf{Encryption Algorithm Speeds}: Implemented RSA and a symmetric key algorithm 
            in Java to compare the execution time of the algorithms.
    \end{asparablank}

\section{\mysidestyle Interests \& Activities}
    \begin{asparablank}
        \item \textbf{WE@RIT Open House Leadership Team}: Part of a team of five of female Computer Engineering students, 
        responsibilities include creating and implementing several activities for an Open House event targeting young women (grades 6-9) 
        to gain hands on experience in engineering.\\
        \item \textbf{Computer Science House (CSH) Member}: A Special Interest House at RIT that
            provides a unique living and learning environment with access to facilities and other resources to promote
            hands-on learning while still maintaining a social atmosphere.\\
        \item \textbf{CSH Director of Evaluations (Spring 2016)}: Responsible for membership evaluations, requirements, and recruitment 
            as well as serving as a liaison between CSH and RIT Residence Life.
    \end{asparablank}
\end{resume}
\end{document}
